Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-13 ch04-lrmhinf/ch04appendices.inc.tex
Some comments from Adam and Tom

\begin{remark}
It should be noted that while the benchmark paper by \citet{Voorhoeve2015SYSID} deals with the same physical \gls{AVIS}, the experimental data of the benchmark is fundamentally different from the data presented here.
\Citet{Voorhoeve2015SYSID} only consider the `physical' \gls{AVIS} with $8$ inputs and $6$ outputs as indicated by the \code{QuanserQ8} block in \figref{fig:avis:simulink:avis} as the system under test.
The measurements of the benchmark data were carried out in open-loop.
Hence, the experimental controller ($\experimental\Controller_{\mathrm{benchmark}} = 0$),the saturations, the filter $F$ and the static matrices $K$ are different.
Moreover, the sample rate of the benchmark data is much higher ($\fs  = 20 \unit{kHz}$) compared to the data in this work ($\fs = 1\unit{kHz}$) thanks to an upgrade of the real-time computer responsible for acquiring the signals.
\end{remark}

>>>>

\begin{remark}
It should be noted that while the benchmark paper by \citet{Voorhoeve2015SYSID} deals with the same physical \gls{AVIS}, the experimental data of the benchmark is fundamentally different from the data presented here.
\Citet{Voorhoeve2015SYSID} only consider the `physical' \gls{AVIS} with $8$ inputs and $6$ outputs as indicated by the \code{QuanserQ8} block in \figref{fig:avis:simulink:avis} as the system under test.
The measurements of the benchmark data were carried out in open-loop.
Hence, the experimental controller ($\experimental\Controller_{\mathrm{benchmark}} = 0$),the saturations, the filter $F$ and the static matrices $K$ are different.
Moreover, the sample rate of the benchmark data is much higher ($\fs  = 20 \unit{kHz}$) compared to the data in this work ($\fs = 1\unit{kHz}$) after an upgrade of the real-time computer responsible for acquiring the signals.
\end{remark}
